A General and Parallel Platform for Mining Co-Movement Patterns over Large-scale Trajectories

### 2016-10-28 Camera-Ready/sec6_experiment.tex
Camera-Ready
Ohohoho

\section{Experimental Study}
\label{sec:exp}
In this section, we evaluate the efficiency and scalability of our proposed parallel GCMP detectors on real trajectory datasets. All the experiments are carried out in a cluster with $12$ nodes, each equipped with four quad-core $2.2$GHz Intel processors, $32$GB memory and gigabit Ethernet.

\textbf{Environment Setup}: We use Yarn\footnote{\url{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}} to manage our cluster. We pick one machine as Yarn's master node, and for each of the remaining machines, we reserve one core and $2$GB memory for Yarn processes. We deploy our GCMP detector on Apache Spark 1.5.2 with the remaining $11$ nodes as the computing nodes.
To fully utilize the computing resources, we configure each node to run five executors, each taking three cores and $5$GB memory. In Spark, one of the $55$ executors is taken as the Application Master for coordination, therefore our setting results in $54$ executors.  We set the number of partitions to be $486$ to fully utilize the multi-threading feature of every core.
All our implementations as well as cluster setups are publicly available% in Github
\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}, we have also experimented with a query-based TRPM using Spark-SQL 2.0.0 window function. 
We find that Spark-SQL fails to execute the query-based TRPM in parallel, which results in a 120x performance slowdown compared to mapreduce-based TRPM.
%
%it runs over 120 times slower than the mapreduce-based TRPM. 
Thus we only report the performance of mapreduce-based TRPM in this paper.}.

\textbf{Datasets}: We use three real trajectory datasets in different application scenarios:
\begin{itemize}[nosep]
\item{Shopping}\footnote{\url{http://www.irc.atr.jp/crest2010_HRI/ATC_dataset/}}: The dataset contains
  trajectories of visitors in the ATC shopping center in Osaka. To better capture the indoor activities, the visitor locations are sampled every half second, resulting in $13,183$ long trajectories. 
\item{GeoLife}\footnote{\url{http://research.microsoft.com/en-us/projects/geolife/}}: The dataset essentially keeps all the travel records of 182 users for a period
of over three years, including multiple kinds of transportation modes (walking, driving and taking public
transportation). For each user, the GPS information is collected periodically and 91 percent of the trajectories
are sampled every 1 to 5 seconds.
\item{Taxi}\footnote{Taxi is our proprietary dataset}: The dataset tracks the trajectories of $15,054$ taxies in Singapore. For each taxi, the GPS information are continually collected for one entire month with the sampling rate around 30 seconds.
\end{itemize}

\textbf{Preprocessing}: We replace timestamps with global sequences (starting from $1$) for each dataset. 
We set a fixed sampling rate for each dataset (i.e., GeoLife = 5 seconds, Shopping=0.5 seconds, Taxi = 30 seconds)
and use linear interpolation to fill missing values.
%For each dataset, we set a fixed sampling rate (CLEARLY STATE THE SAMPLING RATE FOR EACH DATASET) and use linear interpolation to fill missing values. 
%Finally, we obtain a set of trajectories with equal length. 
%Finally, we obtain a set of dense trajectories with equal length. 
For the clustering method, we use DBSCAN~\cite{ester1996density} and customize its two parameters $\epsilon$ (proximity threshold) and $minPt$ (the minimum number of points required to form a dense region). We set $\epsilon=5$, $minPt=10$ for GeoLife and Shopping datasets; and $\epsilon=20$, $minPt=10$ for Taxi dataset. Note that other clustering methods or settings can also be applied. 
%The clustered snapshots are stored in HDFS as $\langle t, S_t \rangle$ pair, where $t$ is the timestamp, $S_t$ contains the clusters at snapshot $t$. 
After preprocessing, the statistics of the three datasets are listed in Table~\ref{exp:dataset}.

%\vspace{-2mm}
\begin{table} [h]
\center
\begin{tabular}{|l|l|l|l|}
\hline
 \textbf{Attributes}& \textbf{Shopping} &  \textbf{GeoLife} &  \textbf{Taxi} \\ 
\hline 
\# objects  & 13,183 & 18,670 & 15,054\\ 
\hline
%\# average ts & 3,114  & 2,924 & 19,667 \\ 
%\hline
\# data points  & 41,052,242 & 54,594,696 & 296,075,837\\ 
\hline
\# snapshots  & 16,931 & 10,699 & 44,364\\ 
\hline
\# clusters  & 211,403  & 206,704& 536,804\\
\hline
avg. cluster size  & 171 & 223 & 484\\
\hline
\end{tabular}
 \vspace{-0.5em}
\caption{Statistics of datasets.}
\vspace{-0.5em}
\label{exp:dataset}
\end{table}

\begin{table}[h]
\small
\begin{tabular}{c|l|p{3cm}}
\hline 
\textbf{Parameter} & \textbf{Meaning} & \textbf{Values} \\ 
\hline 
M & min  objects &  5, 10,  \textbf{15}, 20, 25 \\ 
\hline 
K & min duration & 120, 150, \textbf{180}, 210, 240 \\ 
\hline 
L & min local duration & 10, 20, \textbf{30}, 40,50 \\ 
\hline 
G & max gap & 10, 15, \textbf{20}, 25, 30 \\ 
\hline
$O_r$ & ratio of objects & 20\%,40\%, 60\%, 80\%, \textbf{100\%} \\ \hline
$T_r$ & ratio of snapshots & 20\%,40\%, 60\%, 80\%, \textbf{100\%} \\ \hline
N & number of machines & 1, 3, 5, 7, 9, \textbf{11}\\ 
\hline 
\end{tabular} 
 \vspace{-0.5em}
\caption{Parameters and their default values.}
 \vspace{-0.5em}
\label{tbl:parameters}
\end{table}

%\vspace{-3mm}
\textbf{Parameters}: To systematically study the performance of
our algorithms, we conduct experiments on various parameter settings. The parameters to be evaluated are listed in Table~\ref{tbl:parameters}, with default settings in bold.

@@

    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
        \caption{Taxi vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
        \caption{Taxi vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
        \caption{Taxi vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
        \caption{Taxi vary $G$}
    \end{subfigure}   
	 \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
        \caption{Taxi vary $O_r$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
        \caption{Taxi vary $T_r$}
    \end{subfigure}      
\vspace{-0.5em}
\caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
\vspace{-0.5em}
\label{exp:performance_vary}
\end{figure*}

@@

%The result also reveals the potential of the two solutions to handle larger trajectories. Again, SPARE outperforms TRPM in both execution time and memory usage which dues to the set of effective pruning procedures.

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} % & \textbf{Time} 
& \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
\multirow{2}{*}{Shopping}              & TRPM           % & 597
                               & 90,859                 & 10,019               \\ %\cline{2-5} 
                                       & SPARE           %& 237
                                                                      & 33,638                 & 8,613                \\ \hline
\multirow{2}{*}{Geolife}               & TRPM            %& 747 
                              & 106,428                & 18,454               \\ %\cline{2-5} 
                                       & SPARE           %& 341 
                                                                     & 35,343                 & 14,369               \\ \hline
\multirow{2}{*}{Taxi}                  & TRPM            %& 3,648  
                           & 503,460                & 51,691               \\ %\cline{2-5} 
                                       & SPARE           %& 580  
                                                                    & 68,580                & 35,912               \\ \hline
\end{tabular}
 \vspace{-0.5em}
\caption{Resources taken for TRPM and SPARE. Vcore-seconds is the aggregate of time spent in each core. Memory is the actual size (in MB) of RDDs.}
\vspace{-0.5em}
\label{tbl:resource}
\end{table}

%\begin{figure}[h]
%\centering
%	\begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
%        \caption{Shopping vary $O_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
%        \caption{Geolife vary $O_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
%        \caption{Taxi vary $O_r$}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
%        \caption{Shopping vary $T_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
%        \caption{Geolife vary $T_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
%        \caption{Taxi vary $T_r$}
%    \end{subfigure}
% \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
% \label{exp:performance_vary_OT}
%\end{figure}

%\vspace{-3mm}
\subsection{Analysis of SPARE framework}
In this part, we extensively evaluate SPARE from three aspects:
(1) the advantages brought by the sequence simplification, (2) the effectiveness of load balance, and (3) the scalability with increasing computing resources.
%Then, we study the scalability of SPARE with increasing computing resources.

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|}
\hline 
\textbf{Dataset} & \textbf{Shopping} & \textbf{GeoLife} & \textbf{Taxi} \\ 
\hline 
Before pruning & 878,309 &  1,134,228 & 2,210,101 \\ 
\hline 
After pruning & 76,672 & 123,410 & 270,921 \\ 
\hline 
Prune ratio & 91.2\% & 89.1\% & 87.7\% \\ 
\hline 
\end{tabular} 
\vspace{-0,5em}
\caption{Pruning power of SPARE.}
\vspace{-0,5em}
%\vspace{-4mm}
\label{tbl:pruning}
\end{table}

\begin{figure}[h]
\centering
	  \includegraphics[width=0.4\textwidth]{/exp/spare/detail1.eps}
	 \vspace{-0.5em}
    \caption{Cost breakdown of TRPM, SPARE, SPARE-RD.}
   \vspace{-5mm}
    \label{exp:wl}
\end{figure}

\subsubsection{Load balance}
To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method. In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
Figure~\ref{exp:wl} shows the breakdown of the costs in the mapreduce stages 
for SPARE and SPARE-RD. %\revised{with TRPM as comparison}. 
We observe that the map and shuffle time of SPARE and SPARE-RD are identical. The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost). 
Meanwhile, both SPARE and SPARE-RD outperform TRPM in each phase. This indicates the 
efficiency of the star partition and apriori enumeration.
%\revised{We also report the cost summaries (i.e., longest, shortest and standard deviation) of all jobs for the three methods in Table~\ref{tbl:strags}. As the table shows, SPARE produces more balanced jobs
%than SPARE-RD which verify the effectiveness of the best-fit strategy. In addition, TRPM 
%maintains a low deviation because it uses equal size (i.e., $\eta$) partitioning. 
%However, TRPM still takes much longer time than SPARE algorithms.}
%We also report the cost  for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
We also report the cost of the longest job (Max) and the standard deviation (Std. Dev.)
%\emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) 
for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.

\begin{table}[h]
\centering 
\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
                         & Max        & Std. Dev.     & Max       & Std. Dev.      \\ \hline
Shopping                 & 295              & 41         & 237             & 21       \\ \hline
GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
Taxi                     & 681              & 147        & 580             & 96       \\ \hline
\end{tabular}
%\begin{tabular}{|l|c|c|c|c|}
%\hline
%\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Min} & \textbf{Max} & \textbf{Std. Dev.} 
%\\ \hline%\specialrule{1pt}{-0.5pt}{-0.5pt} 
%\multirow{3}{*}{Shopping}             % & TRPM            &     426                          & 597                 & 35 \\ %\cline{2-5} 
%                                       & SPARE-RD          & 122                               &  295             & 41
%\\% \cline{2-5}                                        
%									   & SPARE           &  134                              &   237               & 21
%\\ \hline                                
%\multirow{3}{*}{GeoLife}             % & TRPM            &    493                            & 747                & 78               \\ %\cline{2-5} 
%                                       & SPARE-RD          &  38                               &   484               & 148
%\\ %\cline{2-5}                                        
%									   & SPARE           &   107                             &     341             & 96
%\\ \hline
%\multirow{3}{*}{Taxi}             % & TRPM            &   3,460                            &    3,648              & 51 \\ %\cline{2-5} 
%                                       & SPARE-RD          & 122                               & 681                 & 109
%\\ %\cline{2-5}                                        
%									   & SPARE           &   134                             &  580                & 56               
%\\ \hline
%\end{tabular}
\vspace{-0.5em}
  \caption{Statistics of execution time (seconds) on all jobs.}
  \vspace{-0.5em}
  \label{tbl:strags}
\end{table}

%\vspace{-5mm}
\subsubsection{Scalability}
When examining SPARE with increasing computing resources (number of machines), we also compare SPARE with the state-of-the-art solutions for \emph{swarm} and \emph{platoon} in the single-node setting. Since the original \emph{swarm} and \emph{platoon} detectors cannot handle very large-scale datasets, we only use 60\% of each dataset for evaluation. For a fair comparisons, we customize two variants of SPARE to mine \emph{swarm}s and \emph{platoon}s, which are denoted as SPARE-S and SPARE-P respectively. The customization is according to the settings in Table~\ref{tbl:patterns} and the results are reported in Figure~\ref{exp:scalability}. 
First, the centralized schemes are not suitable to discover patterns in 
large-scale trajectory databases. It takes nearly $30$ hours to 
detect \emph{swarm}s and $11$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. 
In contrast, when utilizing the multi-core (i.e., a single node with four executors) environment, 
SPARE-P achieves $7$ times speedup and SPARE-S achieves $10$ times speedup. 
%our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively. 
Second, we see that SPARE schemes demonstrate promising scalability in terms of the number of machines available. The running times decrease almost inversely as more machines are used. 
When all the $11$ nodes ($162$ cores) are available, 
SPARE-P is upto $65$ times and SPARE-S is upto $112$ times better than the state-of-the-art centralized schemes.
%than \emph{platoon} and SPARE-S is upto $112$ times better than \emph{swarm}.
%state-of-the-art \emph{platoon} detector in a centralized server.
%
\begin{figure*}[t]
\centering
\begin{subfigure}[b]{0.3\textwidth}
    \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
        \caption{Shopping vary $N$}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
        \caption{GeoLife vary $N$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
        \caption{Taxi vary $N$}
    \end{subfigure}
%\vspace{-0.5em}
 \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM.}
 \label{exp:scalability}
\end{figure*}

>>>>

\section{Experimental Study}
\label{sec:exp}
In this section, we evaluate the efficiency and scalability of our proposed parallel GCMP detectors on real trajectory datasets. All the experiments are carried out in a cluster with $12$ nodes, each equipped with four quad-core $2.2$GHz Intel processors, $32$GB memory and Gigabit Ethernet.

\textbf{Environment Setup}: We use Yarn\footnote{\url{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}} to manage our cluster. We pick one machine as Yarn's master node, and for each of the remaining machines, we reserve one core and $2$GB memory for Yarn processes. We deploy our GCMP detector on Apache Spark 1.5.2\footnote{We have experimented with a query-based TRPM using Spark-SQL 2.0.0 window function. 
We find that Spark-SQL fails to execute the query-based TRPM in parallel, which results in a 120x performance slowdown compared to mapreduce-based TRPM.
Thus we only report the performance of mapreduce-based TRPM in this paper.} with the remaining $11$ nodes as the computing nodes.
To fully utilize the computing resources, we configure each node to run five executors, each taking three cores and $5$GB memory. In Spark, one of the $55$ executors is taken as the Application Master for coordination, therefore our setting results in $54$ executors.  We set the number of partitions to be $486$ to fully utilize the multi-threading feature of every core.
All our implementations as well as cluster setups are publicly available% in Github
\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}.}.

\textbf{Datasets}: We use three real trajectory datasets that are collected from different applications:
\begin{itemize}[nosep]
\item{Shopping}\footnote{\url{http://www.irc.atr.jp/crest2010_HRI/ATC_dataset/}}: The dataset contains
  trajectories of visitors in the ATC shopping center in Osaka. To better capture the indoor activities, the visitor locations are sampled every half second, resulting in $13,183$ long trajectories. 
\item{GeoLife}\footnote{\url{http://research.microsoft.com/en-us/projects/geolife/}}: The dataset essentially keeps all the travel records of 182 users for a period
of over three years, including multiple kinds of transportation modes (walking, driving and taking public
transportation). For each user, the GPS information is collected periodically and 91 percent of the trajectories
are sampled every 1 to 5 seconds.
\item{Taxi}\footnote{Taxi is our proprietary dataset}: The dataset tracks the trajectories of $15,054$ taxies in Singapore. For each taxi, the GPS information are continually collected for one entire month with the sampling rate around 30 seconds.
\end{itemize}

\textbf{Preprocessing}: We replace timestamps with global sequences (starting from $1$) for each dataset. 
We set a fixed sampling rate for each dataset (i.e., GeoLife = 5 seconds, Shopping=0.5 seconds, Taxi = 30 seconds)
and use linear interpolation to fill missing values.
%For each dataset, we set a fixed sampling rate (CLEARLY STATE THE SAMPLING RATE FOR EACH DATASET) and use linear interpolation to fill missing values. 
%Finally, we obtain a set of trajectories with equal length. 
%Finally, we obtain a set of dense trajectories with equal length. 
For the clustering method, we use DBSCAN~\cite{ester1996density} and customize its two parameters $\epsilon$ (proximity threshold) and $minPt$ (the minimum number of points required to form a dense region). We set $\epsilon=5$, $minPt=10$ for GeoLife and Shopping datasets; and $\epsilon=20$, $minPt=10$ for Taxi dataset. 
%Note that other clustering methods or settings can also be applied. 
%The clustered snapshots are stored in HDFS as $\langle t, S_t \rangle$ pair, where $t$ is the timestamp, $S_t$ contains the clusters at snapshot $t$. 
After preprocessing, the statistics of the three datasets are listed in Table~\ref{exp:dataset}.

%\vspace{-2mm}
\begin{table} [h]
\center
\begin{tabular}{|l|l|l|l|}
\hline
 \textbf{Attributes}& \textbf{Shopping} &  \textbf{GeoLife} &  \textbf{Taxi} \\ 
\hline 
\# objects  & 13,183 & 18,670 & 15,054\\ 
\hline
%\# average ts & 3,114  & 2,924 & 19,667 \\ 
%\hline
\# data points  & 41,052,242 & 54,594,696 & 296,075,837\\ 
\hline
\# snapshots  & 16,931 & 10,699 & 44,364\\ 
\hline
\# clusters  & 211,403  & 206,704& 536,804\\
\hline
avg. cluster size  & 171 & 223 & 484\\
\hline
\end{tabular}
%\vspace{-0.5em}
\caption{Statistics of datasets.}
%\vspace{-0.5em}
\label{exp:dataset}
\end{table}

\begin{table}[h]
\begin{tabular}{c|l|p{3.3cm}}
\hline 
\textbf{Param.} & \textbf{Meaning} & \textbf{Values} \\ 
\hline 
M & min  objects &  5, 10,  \textbf{15}, 20, 25 \\ 
\hline 
K & min duration & 120, 150, \textbf{180}, 210, 240 \\ 
\hline 
L & min local duration & 10, 20, \textbf{30}, 40,50 \\ 
\hline 
G & max gap & 10, 15, \textbf{20}, 25, 30 \\ 
\hline
$O_r$ & ratio of objects & 20\%,40\%,60\%,80\%,\textbf{100\%} \\ \hline
%$O_r$ & ratio of objects & 0.2, 0.4, 0.6, 0.8, 1 \\ \hline
$T_r$ & ratio of snapshots & 20\%,40\%,60\%,80\%,\textbf{100\%} \\ \hline
%$T_r$ & ratio of snapshots & 0.2, 0.4, 0.6, 0.8, 1 \\ \hline
N & number of machines & 1, 3, 5, 7, 9, \textbf{11}\\ 
\hline 
\end{tabular} 
%\vspace{-0.5em}
\caption{Parameters and their default values.}
 %\vspace{-0.5em}
\label{tbl:parameters}
\end{table}

\textbf{Parameters}: To systematically study the performance of
our algorithms, we conduct experiments on various parameter settings. The parameters to be evaluated are listed in Table~\ref{tbl:parameters}, with default settings in bold.

@@

    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
        \caption{Taxi vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
        \caption{Taxi vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
        \caption{Taxi vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
        \caption{Taxi vary $G$}
    \end{subfigure}   
	 \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
        \caption{Taxi vary $O_r$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.16\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
        \caption{Taxi vary $T_r$}
    \end{subfigure}      
%\vspace{-0.5em}
\caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
%\vspace{-0.5em}
\label{exp:performance_vary}
\end{figure*}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} 
& \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
\multirow{2}{*}{Shopping}              & TRPM           
                               & 90,859                 & 10,019               \\ 
                                       & SPARE           
                                                                      & 33,638                 & 8,613                \\ \hline
\multirow{2}{*}{Geolife}               & TRPM            
                              & 106,428                & 18,454               \\
                                       & SPARE            
                                                                     & 35,343                 & 14,369               \\ \hline
\multirow{2}{*}{Taxi}                  & TRPM            
                           & 503,460                & 51,691               \\ 
                                       & SPARE           
                                                                    & 68,580                & 35,912               \\ \hline
\end{tabular}
%\vspace{-0.5em}
\caption{Resources taken for TRPM and SPARE. Vcore-seconds is the aggregate of time spent in each core. Memory is the actual size (in MB) of RDDs.}
%\vspace{-0.5em}
\label{tbl:resource}
\end{table}

\subsection{Analysis of SPARE framework}
In this part, we extensively evaluate SPARE from three aspects:
(1) the advantages brought by the sequence simplification, (2) the effectiveness of load balance, and (3) the scalability with increasing computing resources.
%Then, we study the scalability of SPARE with increasing computing resources.

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|}
\hline 
\textbf{Dataset} & \textbf{Shopping} & \textbf{GeoLife} & \textbf{Taxi} \\ 
\hline 
Before pruning & 878,309 &  1,134,228 & 2,210,101 \\ 
\hline 
After pruning & 76,672 & 123,410 & 270,921 \\ 
\hline 
Prune ratio & 91.2\% & 89.1\% & 87.7\% \\ 
\hline 
\end{tabular} 
%\vspace{-0.5em}
\caption{Pruning power of SPARE.}
%\vspace{-0.5em}
\label{tbl:pruning}
\end{table}

%\vspace{1em}
\subsubsection{Load balance}
To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method. In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
Figure~\ref{exp:wl} shows the breakdown of the costs in the mapreduce stages 
for SPARE and SPARE-RD. %\revised{with TRPM as comparison}. 
We observe that the map and shuffle time of SPARE and SPARE-RD are identical. The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost). 
Meanwhile, both SPARE and SPARE-RD outperform TRPM in each phase. This shows the 
efficiency of the star partition and apriori enumeration.
%\revised{We also report the cost summaries (i.e., longest, shortest and standard deviation) of all jobs for the three methods in Table~\ref{tbl:strags}. As the table shows, SPARE produces more balanced jobs
%than SPARE-RD which verify the effectiveness of the best-fit strategy. In addition, TRPM 
%maintains a low deviation because it uses equal size (i.e., $\eta$) partitioning. 
%However, TRPM still takes much longer time than SPARE algorithms.}
%We also report the cost  for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
We also report the cost of the longest job (Max) and the standard deviation (Std. Dev.)
%\emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) 
for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.
%
%\begin{figure}[h]
%\centering
%	  \includegraphics[width=0.4\textwidth]{/exp/spare/detail1.eps}
%	 %\vspace{-0.5em}
%    \caption{Cost breakdown of TRPM, SPARE, SPARE-RD.}
%    \label{exp:wl}
%    %\vspace{-0.5em}
%\end{figure}

%\begin{table*}
%\centering
%\begin{tabular}{|c|c|c|c|}
%\hline
%
%\includegraphics[width=0.4\textwidth]{/exp/spare/detail1.eps}
% &      &       &      \\ \hline
%  & 1     & 2     & 3    \\ \hline
%  & \multicolumn{3}{l|}{}
%\\\hline
%\end{tabular}
%\end{table*}

%\begin{figure*}
%\centering
%\begin{tabular}{cccc}
%\begin{subfigure}[b]{0.22\textwidth}
% \includegraphics[width=\textwidth]{/exp/spare/detail1.eps}
% \caption{Cost breakdown of TRPM, SPARE, SPARE-RD.}   
%\end{subfigure}
% &  \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
%        \caption{Shopping vary $N$}
%    \end{subfigure}    &  \begin{subfigure}[b]{0.22\textwidth}  \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}\caption{GeoLife vary $N$} \end{subfigure}    &   \begin{subfigure}[b]{0.22\textwidth}       \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}\caption{Taxi vary $N$}\end{subfigure}    \\
%       & \multicolumn{3}{c}{}
%\end{tabular}
%\end{figure*}

\begin{figure*}
\begin{minipage}{0.3\textwidth}
\includegraphics[width=\textwidth]{/exp/spare/detail1.eps}
 \caption{Cost breakdown of TRPM, SPARE-RD and SPARE.}
    \label{exp:wl}
\end{minipage}
\begin{minipage}{0.74\textwidth}
\centering
	 \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
        \caption{Shopping vary $N$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
        \caption{GeoLife vary $N$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
        \caption{Taxi vary $N$}
    \end{subfigure} 
 \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM.}
 \label{exp:scalability}
\end{minipage}
\end{figure*}

\begin{table}[h]
\centering 
\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
                         & Max        & Std. Dev.     & Max       & Std. Dev.      \\ \hline
Shopping                 & 295              & 41         & 237             & 21       \\ \hline
GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
Taxi                     & 681              & 147        & 580             & 96       \\ \hline
\end{tabular}
%\vspace{-0.5em}
  \caption{Statistics of execution time (seconds) on all jobs.}
%\vspace{-0.5em}
  \label{tbl:strags}
\end{table}

%\vspace{-5mm}
\subsubsection{Scalability}
When examining SPARE with increasing computing resources (number of machines), we also compare SPARE with the state-of-the-art solutions for \emph{swarm} and \emph{platoon} in the single-node setting. Since the original \emph{swarm} and \emph{platoon} detectors cannot handle very large-scale datasets, we only use 60\% of each dataset for evaluation. For a fair comparisons, we customize two variants of SPARE to mine \emph{swarm}s and \emph{platoon}s, which are denoted as SPARE-S and SPARE-P respectively. The customization is according to the settings in Table~\ref{tbl:patterns} and the results are reported in Figure~\ref{exp:scalability}. 
First, the centralized schemes are not suitable to discover patterns in 
large-scale trajectory databases. It takes nearly $30$ hours to 
detect \emph{swarm}s and $11$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. 
In contrast, when utilizing the multi-core (i.e., a single node with four executors) environment, 
SPARE-P achieves $7$ times speedup and SPARE-S achieves $10$ times speedup. 
%our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively. 
Second, we see that SPARE schemes demonstrate promising scalability in terms of the number of machines available. The running times decrease almost inversely as more machines are used. 
When all the $11$ nodes ($162$ cores) are available, 
SPARE-P is upto $65$ times and SPARE-S is upto $112$ times better than the state-of-the-art centralized schemes.
%than \emph{platoon} and SPARE-S is upto $112$ times better than \emph{swarm}.
%state-of-the-art \emph{platoon} detector in a centralized server.
%
%\begin{figure}[t]
%\centering
%\begin{subfigure}[b]{0.15\textwidth}
%    \includegraphics[width=\textwidth]{/exp/spare/scalability-shopping.eps}
%        \caption{Shopping vary $N$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.15\textwidth}
%        \includegraphics[width=\textwidth]{/exp/spare/scalability-geolife.eps}
%        \caption{GeoLife vary $N$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.15\textwidth}
%        \includegraphics[width=\textwidth]{/exp/spare/scalability-taxi.eps}
%        \caption{Taxi vary $N$}
%    \end{subfigure}
%%\vspace{-0.5em}
% \caption{Comparisons among TRMP, SPARE, PLATOON and SWARM.}
% %\vspace{-0.5em}
% \label{exp:scalability}
%\end{figure}
